\textbf{Computational Fuzzy Extractors}

### 2013-03-19 CompFuzzExt.tex
Cleanup up full rank notation in Theorem 5.3

\begin{figure}[t]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
\item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
\item Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., n$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., n$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $\D$ on input $\vA, \vb$.
\item Output $\D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(we use techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$, thus by union bound this probability is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\beta+\alpha} }= \frac{\alpha}{q^{\beta}} = \ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

>>>>

\begin{figure}[t]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
\item If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns.  Let  $T$ be the set of these indices.
\item Initialize $\vW \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., n$:
\subsubitem Generate $\vW_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vW_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vW\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., n$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1\times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $\D$ on input $\vA, \vb$.
\item Output $\D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $\mathcal{D'}$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $\mathcal{D'}$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times \alpha+\beta}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\beta+\alpha} }= \frac{\alpha}{q^{\beta}} = \ngl(n)\\
\end{align*}
Thus, $\Pr[\rank(\vS) = \alpha] \geq 1-\ngl(n)$.
\end{proof}
\begin{corollary}
$
|\Pr[\D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[\D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}
